Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-11-12 index.qmd
Update index.qmd

XGBoost uses gradient boosting on decision tree algorithms to leverage the combination of multiple very low variance models into one overall prediction. Gradient boosting works sequentially, with the first tree being learned on the known target values, and each subsequent tree being learned on the errors of the tree prior. The algorithm then applies a weighting to each tree based on this boosting to determine how much the tree will contribute towards the final output. The final prediction is obtained by the input data traversing all $n$ weighted trees in the learned ensemble. The trained XGBoost model is used to predict BFI in ungauged catchments based on geospatial and hydroclimate predictor variables (Table \ref{tab-######}##}##}##}. Certain predictors were subdivided according to their areal coverage of each basin (e.g. land cover was divided into 16 subdivisions).

@@

>>>>

XGBoost uses gradient boosting on decision tree algorithms to leverage the combination of multiple very low variance models into one overall prediction. Gradient boosting works sequentially, with the first tree being learned on the known target values, and each subsequent tree being learned on the errors of the tree prior. The algorithm then applies a weighting to each tree based on this boosting to determine how much the tree will contribute towards the final output. The final prediction is obtained by the input data traversing all $n$ weighted trees in the learned ensemble. The trained XGBoost model is used to predict BFI in ungauged catchments based on geospatial and hydroclimate predictor variables (Table \ref{tab-######}##}##}##}##}##}. Certain predictors were subdivided according to their areal coverage of each basin (e.g. land cover was divided into 16 subdivisions).

@@

|                              | n    | R2    | MSE    | RMSE  | MAE   | Nash-Sutcliffe | pbias |
|---------|---------|---------|---------|---------|---------|---------|---------|
| Climate - Monsoon Dominated  | 3345 | 0.707 | 0.0166 | 0.129 | 0.077 | 0.694          | -12.6 |
| Climate - Snowmelt Dominated | 6152 | 0.723 | 0.017  | 0.131 | 0.094 | 0.715          | -3.7  |
| PhysRegion - Basin&Range     | 7754 | 0.749 | 0.018  | 0.133 | 0.089 | 0.741          | -5.9  |
| PhysRegion - CO Plateau      | 1743 | 0.806 | 0.013  | 0.115 | 0.081 | 0.801          | -4.4  |
| Climate - Warm-Wet           | 1613 | 0.690 | 0.015  | 0.124 | 0.081 | 0.679          | -9.9  |
| Climate - Warm-Dry           | 3134 | 0.758 | 0.023  | 0.151 | 0.097 | 0.745          | -8.1  |
| Climate - Cool-Wet           | 3134 | 0.710 | 0.013  | 0.115 | 0.085 | 0.708          | -2.5  |
| Climate - Cool-Dry           | 1616 | 0.809 | 0.014  | 0.118 | 0.082 | 0.803          | -5    |
| Slope - High                 | 4398 | 0.753 | 0.014  | 0.120 | 0.084 | 0.746          | -4.4  |
| Slope - Low                  | 5099 | 0.759 | 0.019  | 0.138 | 0.090 | 0.750          | -6.9  |
